Sparse Function-space Representation \\ of Neural Networks

### 2023-05-24 paper/main.tex
update sec. a

\section{Method details}
\label{app:method}
%
\todo{This reads a bit off, is it grammatically correct?} Key to our method is the ability to compute the dual parameters as in \cref{eq:dual_param}. For general exponential family likelihoods we can derive simpler expressions:
\todo{How does this connect to Eq 5?}
\begin{equation}
 \ell(\sigma(f), y) = -\log p(y \mid f) =  A(f)  - \langle y, f\rangle
\end{equation}
where $A(f)$ is the log partition function and $\sigma(.)$ is the link function. Taking the first and second derivative of the loss in this form then becomes: \todo{Becomes what, to be written?}

 For the Bernoulli distribution with a given link function, typically the sigmoid, $\sigma(f_{\vw}(\vx)):= \sigma(f) = \frac{1}{1+e^f}$. Then, we can write the log probability as
%\begin{equation}
%\begin{aligned}
%	\ell(y, \vf_\vw(\vx)) 
%%	&:= - \log p(y | \sigma(f))) \\
%%	&= -y \log(\sigma(f)) - (1-y) \log(1-\sigma(f))\\
%%	&= -y f + \log(1+e^f) \red{ \left[ = - (\langle f, y\rangle - \log(1+e^f)) \right] }
%\end{aligned}
%\end{equation}

\begin{table}[!ht]
\centering
\begin{tabular}{@{}ccc@{}}
\toprule
Loss        & der 1 & der 2 \\ \midrule
Bernoulli    & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$      \\
Mse         & $y - f$      & $1$       \\
Categorical &  $\textrm{softmax}(f_i) - y_i$     &   $\begin{bmatrix}
		p_1\\ \vdots\\p_k
	\end{bmatrix}$,     \\ \bottomrule
\end{tabular}
\end{table}

>>>>

\section{Method details}
\label{app:method}
%
As shown in \cref{eq:dual_param} in the main paper, our method rely on computation of the dual parameters. We show here how we can derive them in general for the family of exponential likelihoods. By rewriting the loss in the natural form, we have,
\begin{equation}
 \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle
\end{equation}
where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics, and $f$ denotes the neural network output before the link function. 
%given the loss functions we use $t(y) = y$. 
Then, taking the first and second derivatives of the loss in this form become:
\begin{equation}\label{eq:dual_param_app}
  \nabla_{f} - \log p(y_i \mid f) |_{f=f_i} =  - A'(f_i) y_i
  \quad \text{and} \quad
  \nabla^2_{f\!f} - \log p(y_i \mid f) |_{f=f_i} = A''(f_i).
\end{equation}
\todo{check the signs with the main paper}
% The second derivative of the log partition function is easily calculated and
In this section, we provide the derivatives needed for the losses used in this work, \ie, the Gaussian likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.

For regression, the negative log likelihood comes from the Gaussian likelihood, and for a single input it can be written as:
\begin{equation}
	\ell(h(f_i), y_i) = % -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
\end{equation}
where the inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$. Thus, the first and second derivatives are
\begin{equation}
	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} = y_i - f_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1
\end{equation}

% While these equations deal with single output functions, we can extend them to multi output functions, such as for the categorical loss.
%The easiest example to deal with is the Bernoulli loss, where 
%The above formulation can be extended to vector input and outputs, \ie, for the categorical loss. In the following table, we list the likelihoods we use and their dual parameter below:
%\begin{equation}
%\begin{aligned}
%	\ell(y, \vf_\vw(\vx)) 
%%	&:= - \log p(y | \sigma(f))) \\
%%	&= -y \log(\sigma(f)) - (1-y) \log(1-\sigma(f))\\
%%	&= -y f + \log(1+e^f) \red{ \left[ = - (\langle f, y\rangle - \log(1+e^f)) \right] }
%\end{aligned}
%\end{equation}

\begin{table}[!ht]
\centering
\caption{}
\begin{tabular}{@{}cccc@{}}
\toprule
Loss        & $h(\cdot)$ & $\nabla_{f}$ & $\nabla^2_{f\!f}$  \\ \midrule
Bernoulli   & $\sigma(f) = \frac{1}{1 + e^{-f}}$ & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$ \\
MSE         & & $y - f$      & $1$ \\
Categorical & $\mathcal{S}_i(\vf) = \frac{e^{\vf_i}}{\sum_{j=1}^C e^{\vf_j}}$ &  $\begin{bmatrix}
		p_1\\ \vdots\\p_k
	\end{bmatrix}$     &   $\begin{bmatrix}
		p_1\\ \vdots\\p_k
	\end{bmatrix}$ \\ \bottomrule
\end{tabular}
\end{table}
